FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-18 paper.tex
Fix bibliography and makefile

\begin{lstlisting}[language = Julia]
  NaN + 42     -> NaN    # not a kill
  \Inf{} - \Inf{}    -> NaN    # gen, but not a kill
  min(NaN, 42) -> NaN    # not a kill
  NaN < 42     -> false  # NaN kill!
\end{lstlisting}

>>>>

\begin{lstlisting}[language = Julia]
  NaN + 42     -> NaN    # not a kill
  Inf - Inf    -> NaN    # gen, but not a kill
  min(NaN, 42) -> NaN    # not a kill
  NaN < 42     -> false  # NaN kill!
\end{lstlisting}
